\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results }

### 2020-06-06 paper.tex
Fix a few latex mistakes

In the Fig. \ref{fig:DE1} a shows schematic representation of the
experimental setup where porous silicon can be manufactured with GRIN,
taking into account the considerations of the electrode as tip, the
rectangular cell and the sample (silicon wafer) with the largest
rectangular attack area.
In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
divided by three regions A, B and C, dependes in therir porosity i.e.,
High, Medium and Low Porosity. All this corresponding to  expected to
be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
the electrochemical cell with its parts: silicon wafer, teflon cell,
platinum point electrode, electrochemical Aqueous Solution and the
connection of the circuit with the cathode and anode. Finally,
Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
of the electrochemically attacked porous silicon seen from three
different regions as mentioned above. In section 3.1 we give the
details used to carry out our experiments.

@@

	\includegraphics[scale=.3]{../Images/celdan2}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    \textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
    \hline
    A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
    \hline
    B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
    \hline
    C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
    \hline
    A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
    \hline
    B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
    \hline
    C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
    \hline
  \end{tabular}
  \caption{ \emph{We have different points denoted as follows, $ A
      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
      from the sample of a Porous Silicon Microcavity GRIN
      (PSiMCGRIN) $ GMC $. Alternate layers of high refractive index
      (H) and low refractive index (L) are obtained at each of the
      measurement points (A, B and C). The refractive indexes of the
      PSiMCGRIN were considered from the experimental and theoretical
      values that were obtained for the porosity ($ P =
      0.3J^{0.24}$). And we could obtain the attack time with the
      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
$ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
 \begin{figure}
   \centering
   \includegraphics[scale=.5]{Images/MCGRINSEM}
   \caption{\emph{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_{_{i}} =
       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
	\label{fig:MCGRIN4}
\end{figure}

>>>>

In the Fig. \ref{fig:DE1} a shows schematic representation of the
experimental setup where porous silicon can be manufactured with GRIN,
taking into account the considerations of the electrode as tip, the
rectangular cell and the sample (silicon wafer) with the largest
rectangular attack area.
In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
divided by three regions A, B and C, dependes in therir porosity i.e.,
High, Medium and Low Porosity. All this corresponding to  expected to
be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
the electrochemical cell with its parts: silicon wafer, teflon cell,
platinum point electrode, electrochemical Aqueous Solution and the
connection of the circuit with the cathode and anode. Finally,
Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
of the electrochemically attacked porous silicon seen from three
different regions as mentioned above. In section 3.1 we give the
details used to carry out our experiments.

@@

	\includegraphics[scale=.3]{Images/celdan2}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    \textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
    \hline
    A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
    \hline
    B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
    \hline
    C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
    \hline
    A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
    \hline
    B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
    \hline
    C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
    \hline
  \end{tabular}
  \caption{ \emph{We have different points denoted as follows, $ A
      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
      from the sample of a Porous Silicon Microcavity GRIN
      (PSiMCGRIN) $ GMC $. Alternate layers of high refractive index
      (H) and low refractive index (L) are obtained at each of the
      measurement points (A, B and C). The refractive indexes of the
      PSiMCGRIN were considered from the experimental and theoretical
      values that were obtained for the porosity ($ P =
      0.3J^{0.24}$). And we could obtain the attack time with the
      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
$ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
 \begin{figure}
   \centering
   \includegraphics[scale=.5]{Images/MCGRINSEM}
   \caption{\emph{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_{_{i}} =
       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
	\label{fig:MCGRIN4}
\end{figure}
